---
title: "NBA Top 20 All-Time Points Leaders"
author: "Juanma Martinez"
date: "21st October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Set working directory


library(dplyr)
library(plotly)
library(tidyr)
library(scales)
library(readr)

## Upload data set - All_Time_Leaders_Points_Regular_Season  REGULAR SEASON

library(readr)
All_Time_Leaders_Points_Regular_Season <- read_csv("All_Time_Leaders_Points_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Points_Regular_Season)

## add and index column

All_Time_Leaders_Points_Regular_Season_2 <-All_Time_Leaders_Points_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Points_Regular_Season_2 <- All_Time_Leaders_Points_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Points_Regular_Season_2) <- All_Time_Leaders_Points_Regular_Season$PLAYER
head(All_Time_Leaders_Points_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Points_Playoffs <- read_csv("All_Time_Leaders_Points_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Points_Playoffs)



## add and index column

All_Time_Leaders_Points_Playoffs_2 <-All_Time_Leaders_Points_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Points_Playoffs_2 <- All_Time_Leaders_Points_Playoffs[, -(1)]
rownames(All_Time_Leaders_Points_Playoffs_2) <- All_Time_Leaders_Points_Playoffs$PLAYER
head(All_Time_Leaders_Points_Playoffs_2)

```

### Data and Analysis

This document provides an analysis of Top 20 all-time Points leaders in Regular Season and Playoffs in the NBA.

Data source used:

- [NBA](https://stats.nba.com/) 
.
Data downloaded on October 21st 2018

### Top 20 All-Time  Points Leaders in Regular Season



```{r cars,echo=FALSE}
## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Points_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")

```

### Top 20 All-Time  Points Leaders in Playoffs


```{r pressure, echo=FALSE}
d3heatmap(All_Time_Leaders_Points_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Code, questions and feedback

The code for this article is publish in my [github account](https://github.com/JuanmaMN).  - [RPubs link] (http://rpubs.com/Juanma7/431499)

R Packages used 

- d3heatmap
- dplyr
- readr

Please feel free to reach out for any question or feedback.