---
title: "Average points per season - NBA conference"
author: "Juanma Martinez"
date: "4th November 2018"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)


## Setting Working Directory

## Upload the data
library(readr)
library(dplyr)
library(plotly)
library(ggplot2)

NBAstas_Tableau_right <- read_csv("NBAstas_Tableau-right.csv")
View(NBAstas_Tableau_right)
colnames(NBAstas_Tableau_right)

EWCAverage_ggplot2<-NBAstas_Tableau_right%>%   group_by(Conference, Season_1)%>%   summarize(average=mean(round(PTS),6))
View(EWCAverage_ggplot2)

```

### Data and Analysis

Average points per season by each  NBA conference over the last nine seasons.

* Data source used:

    + [NBA](https://stats.nba.com/) 


* Data downloaded on October 21st 2018

* R packages used

    + [plotly](https://plot.ly/feed/) for the graph
    
    + [Dplyr](https://dplyr.tidyverse.org/)
    
    + readr to upload the data set
    


### NBA Conference - Average Points per season

The following plotly graphs contains the average number of points each NBA conference made per season.

We can compare which conference made the highest average number of points by hovering over on each coloured bar.

I have used plotly graph. For full code, please see my Github account or contact me.


**Western and Eastern Conference**


```{r cars, echo= FALSE, warning = FALSE}

p <- plot_ly(EWCAverage_ggplot2, x = ~average, y = ~Season_1, type = 'bar', orientation = 'h', color = ~Conference, 
             text = ~paste('Conference: ', Conference, '</br> Season: ', Season_1,
                           '</br> Average Points: ', average)
             )%>%
  layout(title ="NBA Conference -- Average Points per season",
         barmode = 'stack',
         yaxis = list(title = ""), 
         xaxis = list(title = "Average Points"))

p
```


### Code, questions and feedback

The code for this article is publish in my [github account](https://github.com/JuanmaMN).  

For [RPubs link](http://rpubs.com/Juanma7/436813)


Please feel free to reach out for any question or feedback.
