---
title: "All-time best players by stats: Regular Season VS Playoffs"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)

## Set working directory


library(dplyr)
library(plotly)
library(tidyr)
library(scales)
library(readr)

## Upload data set - All_Time_Leaders_Points_Regular_Season  REGULAR SEASON

library(readr)
All_Time_Leaders_Points_Regular_Season <- read_csv("All_Time_Leaders_Points_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Points_Regular_Season)

## add and index column

All_Time_Leaders_Points_Regular_Season_2 <-All_Time_Leaders_Points_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Points_Regular_Season_2 <- All_Time_Leaders_Points_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Points_Regular_Season_2) <- All_Time_Leaders_Points_Regular_Season$PLAYER
head(All_Time_Leaders_Points_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Points_Playoffs <- read_csv("All_Time_Leaders_Points_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Points_Playoffs)



## add and index column

All_Time_Leaders_Points_Playoffs_2 <-All_Time_Leaders_Points_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Points_Playoffs_2 <- All_Time_Leaders_Points_Playoffs[, -(1)]
rownames(All_Time_Leaders_Points_Playoffs_2) <- All_Time_Leaders_Points_Playoffs$PLAYER
head(All_Time_Leaders_Points_Playoffs_2)

All_Time_Leaders_Assists_Regular_Season <- read_csv("All_Time_Leaders_Assists_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Assists_Regular_Season)

## add and index column

All_Time_Leaders_Assists_Regular_Season_2 <-All_Time_Leaders_Assists_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Assists_Regular_Season_2 <- All_Time_Leaders_Assists_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Assists_Regular_Season_2) <- All_Time_Leaders_Assists_Regular_Season$PLAYER
head(All_Time_Leaders_Assists_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Assists_Playoffs <- read_csv("All_Time_Leaders_Assists_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Assists_Playoffs)



## add and index column

All_Time_Leaders_Assists_Playoffs_2 <-All_Time_Leaders_Assists_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Assists_Playoffs_2 <- All_Time_Leaders_Assists_Playoffs[, -(1)]
rownames(All_Time_Leaders_Assists_Playoffs_2) <- All_Time_Leaders_Assists_Playoffs$PLAYER
head(All_Time_Leaders_Assists_Playoffs_2)

All_Time_Leaders_Field_Goals_Made_Regular_Season <- read_csv("All_Time_Leaders_Field_Goals_Made_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Field_Goals_Made_Regular_Season)

## add and index column

All_Time_Leaders_Field_Goals_Made_Regular_Season_2 <-All_Time_Leaders_Field_Goals_Made_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Field_Goals_Made_Regular_Season_2 <- All_Time_Leaders_Field_Goals_Made_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Field_Goals_Made_Regular_Season_2) <- All_Time_Leaders_Field_Goals_Made_Regular_Season$PLAYER
head(All_Time_Leaders_Field_Goals_Made_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Field_Goals_Made_Playoffs <- read_csv("All_Time_Leaders_Field_Goals_Made_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Field_Goals_Made_Playoffs)



## add and index column

All_Time_Leaders_Field_Goals_Made_Playoffs_2 <-All_Time_Leaders_Field_Goals_Made_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Field_Goals_Made_Playoffs_2 <- All_Time_Leaders_Field_Goals_Made_Playoffs[, -(1)]
rownames(All_Time_Leaders_Field_Goals_Made_Playoffs_2) <- All_Time_Leaders_Field_Goals_Made_Playoffs$PLAYER
head(All_Time_Leaders_Field_Goals_Made_Playoffs_2)

All_Time_Leaders_Rebounds_Regular_Season <- read_csv("All_Time_Leaders_Rebounds_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Rebounds_Regular_Season)

## add and index column

All_Time_Leaders_Rebounds_Regular_Season_2 <-All_Time_Leaders_Rebounds_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Rebounds_Regular_Season_2 <- All_Time_Leaders_Rebounds_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Rebounds_Regular_Season_2) <- All_Time_Leaders_Rebounds_Regular_Season$PLAYER
head(All_Time_Leaders_Rebounds_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Rebounds_Playoffs <- read_csv("All_Time_Leaders_Rebounds_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Rebounds_Playoffs)



## add and index column

All_Time_Leaders_Rebounds_Playoffs_2 <-All_Time_Leaders_Rebounds_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Rebounds_Playoffs_2 <- All_Time_Leaders_Rebounds_Playoffs[, -(1)]
rownames(All_Time_Leaders_Rebounds_Playoffs_2) <- All_Time_Leaders_Rebounds_Playoffs$PLAYER
head(All_Time_Leaders_Rebounds_Playoffs_2)

All_Time_Leaders_Steals_Regular_Season <- read_csv("All_Time_Leaders_Steals_Regular_Season.csv", 
                                                   col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                                    `3 Point Field Goals Made` = col_number(), 
                                                                    `3 Point Field Goals Percentage` = col_number(), 
                                                                    Assists = col_number(), Blocks = col_number(), 
                                                                    `Defensive Rebounds` = col_number(), 
                                                                    `Effective Field Goal Percentage` = col_number(), 
                                                                    `Field Goal Percentage` = col_number(), 
                                                                    `Field Goals Attempted` = col_number(), 
                                                                    `Field Goals Made` = col_number(), 
                                                                    `Free Throw Percentage` = col_number(), 
                                                                    `Free Throws Attempted` = col_number(), 
                                                                    `Free Throws Made` = col_number(), 
                                                                    `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                                    `Offensive Rebounds` = col_number(), 
                                                                    Points = col_number(), Rebounds = col_number(), 
                                                                    Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                                    Turnovers = col_number()))
head(All_Time_Leaders_Steals_Regular_Season)

## add and index column

All_Time_Leaders_Steals_Regular_Season_2 <-All_Time_Leaders_Steals_Regular_Season %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Steals_Regular_Season_2 <- All_Time_Leaders_Steals_Regular_Season[, -(1)]
rownames(All_Time_Leaders_Steals_Regular_Season_2) <- All_Time_Leaders_Steals_Regular_Season$PLAYER
head(All_Time_Leaders_Steals_Regular_Season_2)

## Upload second data set PLAYOFFS

library(readr)
All_Time_Leaders_Steals_Playoffs <- read_csv("All_Time_Leaders_Steals_Playoffs.csv", 
                                             col_types = cols(`3 Point Field Goals Attempted` = col_number(), 
                                                              `3 Point Field Goals Made` = col_number(), 
                                                              `3 Point Field Goals Percentage` = col_number(), 
                                                              Assists = col_number(), Blocks = col_number(), 
                                                              `Defensive Rebounds` = col_number(), 
                                                              `Effective Field Goal Percentage` = col_number(), 
                                                              `Field Goal Percentage` = col_number(), 
                                                              `Field Goals Attempted` = col_number(), 
                                                              `Field Goals Made` = col_number(), 
                                                              `Free Throw Percentage` = col_number(), 
                                                              `Free Throws Attempted` = col_number(), 
                                                              `Free Throws Made` = col_number(), 
                                                              `Games Played` = col_number(), `Minutes Played` = col_number(), 
                                                              `Offensive Rebounds` = col_number(), 
                                                              Points = col_number(), Rebounds = col_number(), 
                                                              Steals = col_number(), `True Shooting Percentage` = col_number(), 
                                                              Turnovers = col_number()))
View(All_Time_Leaders_Steals_Playoffs)



## add and index column

All_Time_Leaders_Steals_Playoffs_2 <-All_Time_Leaders_Steals_Playoffs %>% mutate(id = row_number())

## Pass the first column to the number


library(dplyr)
All_Time_Leaders_Steals_Playoffs_2 <- All_Time_Leaders_Steals_Playoffs[, -(1)]
rownames(All_Time_Leaders_Steals_Playoffs_2) <- All_Time_Leaders_Steals_Playoffs$PLAYER
head(All_Time_Leaders_Steals_Playoffs_2)
```

All-time top scorers {data-orientation=rows}
=====================================  

Column {data-width=200, data-height=300}
-------------------------------------

###

**Top 20 All-Time  Points Leaders in Regular Season and Playoffs**

NBA Stats Analysis of the Top 20 All-time Points Leaders. Stats for Regular Season and Playoffs where we can see how much each player contributes to the different games in which they played.

This analysis contains data until October 21st 2018.

I've used the d3heatmap which easily represents all the players stats. We can hover over on it to see the name of the player, the stats and value.

###

**Code, questions and feedback**

* Data source used: [NBA](https://stats.nba.com/) 

* Data downloaded on October 21st 2018

* R packages used: [d3heatmap](https://cran.r-project.org/web/packages/d3heatmap/index.html) for the graph,  [Dplyr](https://dplyr.tidyverse.org/) and [readr](https://cran.r-project.org/web/packages/readr/README.html) to upload the data set

Column {data-width=800, data-height=700}
-------------------------------------

### Top 20 All-Time  Points Leaders in Regular Season

```{r echo=FALSE}

## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Points_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Top 20 All-Time  Points Leaders in Playoffs


```{r echo=FALSE}

d3heatmap(All_Time_Leaders_Points_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```

All-time Assists Leaders {data-orientation=rows}
=====================================  

Column {data-width=200, data-height=300}
-------------------------------------

###

**Top 20 All-Time Assists Leaders in Regular Season**

NBA Stats Analysis of the Top 20 All-time Assists Leaders. Stats for Regular Season and Playoffs where we can see how much each player contributes to the different games in which they played.

This analysis contains data until October 21st 2018.

I've used the d3heatmap which easily represents all the players stats. We can hover over on it to see the name of the player, the stats and value.


###

**Top 20 All-Time Assists Leaders in Playoffs**

* Data source used: [NBA](https://stats.nba.com/) 

* Data downloaded on October 21st 2018

* R packages used: [d3heatmap](https://cran.r-project.org/web/packages/d3heatmap/index.html) for the graph,  [Dplyr](https://dplyr.tidyverse.org/) and [readr](https://cran.r-project.org/web/packages/readr/README.html) to upload the data set

Column {data-width=800, data-height=700}
-------------------------------------

### Top 20 All-Time  Assists Leaders in Regular Season

```{r echo=FALSE}

## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Assists_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Top 20 All-Time  Assists Leaders in Playoffs


```{r echo=FALSE}

d3heatmap(All_Time_Leaders_Assists_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



All-time FGM Leaders {data-orientation=rows}
=====================================  

Column {data-width=200, data-height=300}
-------------------------------------

###

**Top 20 All-Time  Field Goals Made Leaders in Regular Season**

NBA Stats Analysis of the Top 20 All-time FGM Leaders. Stats for Regular Season and Playoffs where we can see how much each player contributes to the different games in which they played.

This analysis contains data until October 21st 2018.

I've used the d3heatmap which easily represents all the players stats. We can hover over on it to see the name of the player, the stats and value.


###

**Top 20 All-Time  Field Goals Made Leaders in Playoffs**

* Data source used: [NBA](https://stats.nba.com/) 

* Data downloaded on October 21st 2018

* R packages used: [d3heatmap](https://cran.r-project.org/web/packages/d3heatmap/index.html) for the graph,  [Dplyr](https://dplyr.tidyverse.org/) and [readr](https://cran.r-project.org/web/packages/readr/README.html) to upload the data set.

Column {data-width=800, data-height=700}
-------------------------------------

### Top 20 All-Time  Field Goals Made Leaders in Regular Season

```{r echo=FALSE}

## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Field_Goals_Made_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Top 20 All-Time  Field Goals Made Leaders in Playoffs


```{r echo=FALSE}

d3heatmap(All_Time_Leaders_Field_Goals_Made_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```


All-time Rebounds Leaders {data-orientation=rows}
=====================================  

Column {data-width=200, data-height=300}
-------------------------------------

###

**Top 20 All-Time  Rebounds Leaders in Regular Season**

NBA Stats Analysis of the Top 20 All-time Rebounds Leaders. Stats for Regular Season and Playoffs where we can see how much each player contributes to the different games in which they played.

This analysis contains data until October 21st 2018.

I've used the d3heatmap which easily represents all the players stats. We can hover over on it to see the name of the player, the stats and value.


###

**Top 20 All-Time  Rebounds Leaders in Playoffs**

* Data source used: [NBA](https://stats.nba.com/) 

* Data downloaded on October 21st 2018

* R packages used: [d3heatmap](https://cran.r-project.org/web/packages/d3heatmap/index.html) for the graph,  [Dplyr](https://dplyr.tidyverse.org/) and [readr](https://cran.r-project.org/web/packages/readr/README.html) to upload the data set.

Column {data-width=800, data-height=700}
-------------------------------------

### Top 20 All-Time  Rebounds Leaders in Regular Season

```{r echo=FALSE}

## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Rebounds_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Top 20 All-Time  Rebounds Leaders in Playoffs


```{r echo=FALSE}

d3heatmap(All_Time_Leaders_Rebounds_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```

All-time Steals Leaders {data-orientation=rows}
=====================================  

Column {data-width=200, data-height=300}
-------------------------------------

###

**Top 20 All-Time  Steals Leaders in Regular Season**

NBA Stats Analysis of the Top 20 All-time Steals Leaders. Stats for Regular Season and Playoffs where we can see how much each player contributes to the different games in which they played.

This analysis contains data until October 21st 2018.

I've used the d3heatmap which easily represents all the players stats. We can hover over on it to see the name of the player, the stats and value.


###

**Top 20 All-Time  Steals Leaders in Playoffs**

* Data source used: [NBA](https://stats.nba.com/) 

* Data downloaded on October 21st 2018

* R packages used: [d3heatmap](https://cran.r-project.org/web/packages/d3heatmap/index.html) for the graph,  [Dplyr](https://dplyr.tidyverse.org/) and [readr](https://cran.r-project.org/web/packages/readr/README.html) to upload the data set.

Column {data-width=800, data-height=700}
-------------------------------------

### Top 20 All-Time  Steals Leaders in Regular Season

```{r echo=FALSE}

## Heatmap


library(d3heatmap)
d3heatmap(All_Time_Leaders_Steals_Regular_Season_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



### Top 20 All-Time  Steals Leaders in Playoffs


```{r echo=FALSE}

d3heatmap(All_Time_Leaders_Steals_Playoffs_2, scale = "column", colors = "GnBu", dendrogram = "none", 
          
          xaxis_font_size = "7pt", yaxis_font_size = "7pt", show_legend = show.legend,main = "NBA")
```



