---
title: "Wins comparison over the last four seasons"
author: "Juanma Martinez"
date: "21st October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Setting Working Directory

## Upload the data

library(readr)
library(dplyr)
library(plotly)
NBAstas_Tableau_right <- read_csv("NBAstas_Tableau-right.csv")
View(NBAstas_Tableau_right)
colnames(NBAstas_Tableau_right)

NBA_stats_5_seasons_Eastern<-filter(NBAstas_Tableau_right, Season_1 %in% c("2013-2014", "2014-2015",
                                                        "2016-2017", "2017-2018") 
                       & Conference=="Eastern Conference")

NBA_stats_5_seasons_Western<-filter(NBAstas_Tableau_right, Season_1 %in% c("2013-2014", "2014-2015",
                                                                           "2016-2017", "2017-2018") 
                                    & Conference=="Western Conference")

```


### Data and Analysis

Number of games won season over the last four seasons in the NBA.

* Data source used:

    + [NBA](https://stats.nba.com/) 


* Data downloaded on October 21st 2018

* Plotly graphs used.

    + Hover over one point in the scatter plot to see the stats for that specific team.

    +  Click on one season on the legend to hide the stats for that specific season.



### NBA Stats - Wins over season - Eastern Conference


In the following plotly graph, we can see the number of games each team won over the last four seasons.

**Teams in Eastern Conference**


```{r cars, echo=FALSE}
plot_ly(NBA_stats_5_seasons_Eastern, 
        x = ~W, 
        y = ~TEAM,
        color=~Season_1,
        text =  ~paste('</br> Team: ', TEAM,
                       '</br> Season: ', Season_1,
                       '</br> Total Wins: ', W,
                       '</br> Avg. Points: ', PTS),
        hoverinfo = "text",
        type='scatter',
        mode = 'markers') %>%
  layout(xaxis = list(range = c(10, 80), yaxis= "", title = 'Wins'),
          yaxis = list(title = " "))
                      
```


### NBA Stats - Wins over season - Western Conference


In the following plotly graph, we can see the number of games each team won over the last four seasons.

**Teams in Western Conference**



```{r pressure, echo=FALSE}
plot_ly(NBA_stats_5_seasons_Western, 
        x = ~W, 
        y = ~TEAM,
        color=~Season_1,
        text =  ~paste('</br> Team: ', TEAM,
                       
                       '</br> Season: ', Season_1,
                       
                       '</br> Total Wins: ', W,
                       
                       '</br> Avg. Points: ', PTS),
        
        hoverinfo = "text",
        
        type='scatter',
        
        mode = 'markers') %>%
  
  layout(xaxis = list(range = c(10, 80), yaxis= "", title = 'Wins'),
          yaxis = list(title = " "))
```

### Code, questions and feedback

The code for this article is publish in my [github account](https://github.com/JuanmaMN).  

For [RPubs link](http://rpubs.com/Juanma7/431945)

R Packages used 

- plotly
- dplyr
- readr

Please feel free to reach out for any question or feedback.